---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rnotion

<!-- badges: start -->

<!-- badges: end -->

The goal of Rnotion is to bridge R to [Notion](notion.so)'s beta [API](https://developers.notion.com/reference/get-databases) through R-friendly functions. Behind the scene, Rnotion has utilized the power of packages like httr and jsonlite for connectivity, and simulated json-API object using vctrs.

Disclaimers: I've nothing to do with notion team at all. The packages has been built just for the sake of learning.

### Current Project Status

I aim to do things step by step:

1.  Build S3 vectors for each object used in GET and POST in each API - e.g. filter_object, sort_object
2.  Build primitive API-connected functions to interact with Notion
3.  Build content extraction functions to translate the response in a user friendly ways
4.  Build a easy to user wrapper function

| Nope | Under Construction | Somewhat finish                                                     | Wrapper fn available |
|------|--------------------|---------------------------------------------------------------------|----------------------|
|      |                    | [Retrieve a user](https://developers.notion.com/reference/get-user) |                      |
|      |                    |                                                                     |                      |
|      |                    |                                                                     |                      |

## Installation

You can install the released version of Rnotion from [CRAN](https://CRAN.R-project.org) with:

``` r
# Not Yet
# install.packages("Rnotion")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Songyosr/Rnotion")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE, include=FALSE}
library(Rnotion)
## basic example code
set_notion_token(token = ....YOUR_TOKEN_HERE...)
```

```{r cars}
notion_get_user()
notion_get_database()
```
